\documentclass{uofsthesis-cs}

% Documentation for the uofsthesis-cs class is given in uofsthesis-cs.dvi
% 
% It is recommended that you read the CGSR thesis preparation
% guidelines before proceeding.
% They can be found at http://www.usask.ca/cgsr/thesis/index.htm

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FRONTMATTER - In this section, specify information to be used to
% typeset the thesis frontmatter.
  \usepackage{graphicx} 
\usepackage{cite}   
\usepackage{url}  
\usepackage{todonotes}
\usepackage{textcomp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% THESIS TITLE
% Specify the title. Set the capitalization how you want it.
\title{SynVisio: A Multiscale Tool for Visualizing Genomic Conservation}

% AUTHOR'S NAME
% Your name goes here.
\author{Venkat Kiran Bandi}

% DEGREE SOUGHT.  
% Use \MSc or \PhD here
\degree{\MSc}         

% THESIS DEFENCE DATE
% Should be month/year, e.g. July 2004
\defencedate{April/2020}


% NAME OF ACADEMIC UNIT
%
% The following two commands allow you to specify the academic unit you belong to.
% This will appear on the title page as
% ``<academic unit> of <department>''.
% So if you are in the division of biomedical engineering you would need to do:
% \department{Biomedical Engineering}
% \academicunit{Division}
%
% The default is ``Department of Computer Science'' if these commands
% are not given.
%
% If you are in a discipline other than Computer Science, uncomment the following line and
% specify your discipline/department.  Default is 'Computer Science'.
% \department{If not Computer Science, put the name of your department here}

% If you are not in a department, but say, a division, uncomment the following line.
% \academicunit{Put the type of academic unit you belong to here, e.g. Division, College}


% PERMISSION TO USE ADDRESS
%
% If you are not in Comptuer Science you will want to change the
% address on the Permission to Use page.  This is done using the
% \ptuaddress{}.  Example:
%
% \ptuaddress{Head of the Department of Computer Science\\
% 176 Thorvaldson Building\\
% 110 Science Place\\
% University of Saskatchewan\\
% Saskatoon, Saskatchewan\\
% Canada\\
% S7N 5C9
% }

% ABSTRACT
\abstract{
Due to rapid advancements in sequencing technologies high resolution genomic data is readily available for a wide range of species. However, analysing this huge volume of data is still a tedious task. While most genomic analysis tasks can be automated some still require human judgement and manual interpretation. One example of such a task is synteny analysis. Synteny is a key tool in comparative genomic research - it is the study of homologous regions within chromosomes of the same or different species. Visualizing synteny can help researchers in understanding the \textbf{location, size and orientation} of shared sequences among genomes of interest. However, the current tools which exist for synteny analysis are stand-alone programs or command line tools that are difficult to use and that offer very little interactivity. In this paper we provide a decentralized web-based environment for browsing syntenic blocks with multiple visual representations in the form of linear charts, hive charts and dot plots. Our tool also makes it easy to save and revisit graphs so that researchers can iteratively refine their plots and compare them with previous revisions for changes. We present SynVisio, a multiscale synteny analysis tool that provides multiple visualizations of genome collinearity for easy exploration across different scales from the whole genome level all the way down to the individual gene block level.
}

% THESIS ACKNOWLEDGEMENTS -- This can be free-form.

\acknowledgements{

I would like to express my heartfelt gratitude to my supervisor Carl Gutwin, for constantly offering me support both academically and personally, and guiding me towards a field of research that was fantastic to explore and learn.

I am particularly grateful to Gwen Lancaster for her support when I joined the program and am also grateful to my lab mates and all the staff members of the Department of Computer Science that have helped me along the way. 

This project would not have been possible without the constant support of Isobel Parkin, Andrew Sharpe, Kirstin Bett, and Kevin Koh. I would like to thank them for offering their feedback through countless meetings and providing me access to invaluable datasets. Also, I would like to thank members of my thesis committee, Ian McQuillan and Debajyoti Mondal, whose comments and suggestions have greatly improved this manuscript. 

Finally, I would like to thank Canada for offering me a chance at a fresh start and I acknowledge the support of my family and friends for helping me along this journey in starting a new life.

}

% THESIS DEDICATION -- Also free-form.  If you don't want a dedication, comment out the following
% line.
\dedication{

\begin{center}
\textit{This thesis is dedicated to my Mom and Dad for their unconditional love and support.}
\end{center}

}

% LIST OF ABBREVIATIONS - Sample  
% If you don't want a list of abbreviations, comment the following 4 lines.
\loa{
\abbrev{DNA}{Deoxyribonucleic Acid}
\abbrev{RNA}{Ribonucleic Acid}
\abbrev{mRNA}{Messenger RNA}
\abbrev{FASTA}{Fast All}
\abbrev{SVG}{Scalable Vector Graphics}
\abbrev{BLAST}{Basic Local Alignment Search Tool}
\abbrev{GFF}{General Feature Format}
\abbrev{CNV}{Copy Number Variation}
\abbrev{SNP}{Single Nucleotide Polymorphism}
\abbrev{DOM}{Document Object Model}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF FRONTMATTER SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Typeset the title page
\maketitle

% Typeset the frontmatter.  
\frontmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIRST CHAPTER OF THESIS BEGINS HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{root/chapter_1_introduction.tex}
\input{root/chapter_2_related_work.tex}
\input{root/chapter_3_requirement_analysis.tex}
\input{root/chapter_4_visual_design.tex}
\input{root/chapter_5_synvisio.tex}
\input{root/chapter_6_evaluation.tex}
\input{root/chapter_7_discussion.tex}
\input{root/chapter_8_conclusion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUBSEQUENT CHAPTERS (or \input's)  GO HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Bibliograpy should go here. BEFORE appendices!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Typeset the Bibliography.  The bibliography style used is "plain".
% Optionally, you can specify the bibliography style to use:
% \uofsbibliography[stylename]{yourbibfile}
\uofsbibliography{reference.bib}

% If you are not using bibtex, comment the line above and uncomment
% the line below.  
%Follow the line below with a thebibliography environmentand bibitems.  
% Note: use of bibtex is usually the preferred method.

%\uofsbibliographynobibtex


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDICES
%
% Any chapters appearing after the \appendix command get numbered with
% capital letters starting with appendix 'A'.
% New chapters from here on will be called 'Appendix A', 'Appendix B'
% as opposed to 'Chapter 1', 'Chapter 2', etc.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Activate thesis appendix mode.
\uofsappendix

% Put appendix chapters in the appendices environment so that they appear correcty
% in the table of contents.  You can use \input's here as well.
\begin{appendices}

\chapter{Exploring Conservation in Canola}

Step by Step images showing the different features of SynVisio in its current form.

\chapter{Exploring Conservation in Wheat}

Step by Step images showing the different features of SynVisio in its current form.

\chapter{Exploring Conservation in Chickpea}

Step by Step images showing the different features of SynVisio in its current form.

\end{appendices}

\end{document}
